Approximation as Differentiation

### 2025-05-08 main/formal-structures.tex
Recap functor categories [X, C] where X a set.

\begin{definition}[Category of $X$-indexed families of objects]
\label{def:fam:Fam}
For any set $X$ (interpreted as a discrete category) and any category $\cat{C}$, recall that the functor
category $\Func{X}{C}$ has as objects all functors $X \to \cat{C}$, in other words all $X$-indexed families of
objects of $\cat{C}$, and as morphisms from $X \to \cat{C}$ to $Y \to \cat{C}$, all natural transformations,
i.e.~families of morphisms $f_x: X_x \to Y_x$ in $\cat{C}$ for every $x \in X$.
\end{definition}

>>>>

\begin{definition}[Category of $X$-indexed families of objects]
\label{def:fam:Fam}
For any set $X$ (interpreted as a discrete category) and any category $\cat{C}$, recall that the functor
category $\Func{X}{C}$ has as objects all functors $X \to \cat{C}$, in other words all $X$-indexed families of
objects of $\cat{C}$, and as morphisms from $X \to \cat{C}$ to $Y \to \cat{C}$, all families of morphisms
$f_x: X_x \to Y_x$ in $\cat{C}$ for every $x \in X$, with naturality in $X$ immediate.
\end{definition}
